Figures and results for main manuscript

### 2020-08-12 analysis/reports/manuscript_main.Rmd
textual updates
rarefaction

---
title: "Figures and results for main manuscript"
output: 
    github_document:
       df_print: kable
---

@@

>>>>

---
title: "Figures and results for main manuscript"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
geom_histogram() +
  theme_bw() +
facet_wrap(vars(dat), scales = "free_y")
